\documentclass[a4paper,9pt]{article}
\usepackage{latexsym}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{margin=0.7in}
\titleformat{\section}{\large\bfseries}{}{0em}{}
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, itemsep=0pt, topsep=0pt}

\begin{document}

\begin{center}
    {\Large \textbf{Omar Hany Abdelmonem Ahmed}}\\
    \href{mailto:omarhany.212@yahoo.com}{omarhany.212@yahoo.com} \quad | \quad +49 175 4575014 \quad | \quad Berlin \quad | \quad \href{https://github.com/omah03}{github.com/omah03}
\end{center}

\section*{Profile}
Computer Science student with experience in backend systems, ML workflows, and full-stack development. Focused on backend engineering and distributed systems.

\section*{Projects}

\textbf{BVG Real-Time Transit Tracker} \hfill \textit{Java, Spring Boot, JavaScript, Docker} \\
\begin{itemize}
    \item Real-time Berlin transit tracking with live vehicle locations and interactive mapping.
    \item Spring Boot backend with BVG API integration, deployed on Railway cloud platform.
    \item \href{https://bvgsim-production.up.railway.app}{\texttt{Live Demo}} | \href{https://github.com/omah03/BVGSim}{\texttt{GitHub}}
\end{itemize}

\textbf{J.A.R.V.I.S Chatbot} \hfill \textit{React, Node.js, OpenAI, WebSockets} \\
\begin{itemize}
    \item Real-time voice chatbot with OpenAI integration and speech recognition.
    \item WebSocket backend with React frontend for seamless voice interactions.
    \item \href{https://github.com/omah03/J.A.R.V.I.S}{\texttt{GitHub}}
\end{itemize}

\textbf{ML Workflow Platform} \hfill \textit{Python, Flask, React, Docker} \\
\begin{itemize}
    \item Interactive ML pipeline platform for neural network competitions, used by 200+ students.
    \item Cut workflow setup time by 40\% with automated pipeline management.
\end{itemize}

\section*{Experience}

\textbf{Fraunhofer Heinrich-Hertz-Institut} \hfill Berlin, Germany \\
\textit{Working Student – ML \& Software Engineering} \hfill Apr 2024 – Present
\begin{itemize}
    \item Built C++ modules for 3D texturing, cutting latency by 40\%.
    \item Created Python compression tool saving 10TB storage; deployed ML inference with Docker.
    \item Developed real-time LED control system for studio lighting with WebSocket remote control.
\end{itemize}

\textbf{Fraunhofer IPK} \hfill Berlin, Germany \\
\textit{Computer Vision Intern} \hfill Mar – Apr 2024
\begin{itemize}
    \item Automated image annotation using OpenCV and YOLOv8, improved detection by 30\%.
\end{itemize>

\section*{Education}

\textbf{Freie Universität Berlin} \hfill \textit{Oct 2021 – Present} \\
B.Sc. in Computer Science

\section*{Skills}

\textbf{Languages:} Python, C/C++, JavaScript, Java, SQL \\
\textbf{Tools:} Docker, Git, AWS, PyTorch, OpenCV, Linux \\
\textbf{Concepts:} REST APIs, Unit Testing, CI/CD, Agile, OOP

\end{document}
